biological data preperation

### 2018-11-16 src/biological_data_prep.Rmd
nao correct
amo done

amo_yrmt <- amo_yrmt[order(amo_yrmt$year),]
amo_yrmt
```
rename time to month.. and value to amo_sample
```{r}
colnames(amo_yrmt)[2] <- "month"
colnames(amo_yrmt)[3] <- "amo_sample"
amo_yrmt
```

@@

nao_yrmt <- nao_yrmt[order(amo_yrmt$year),]
nao_yrmt
```

>>>>

amo_yrmt <- amo_yrmt[order(amo_yrmt$year),]
amo_yrmt
```
rename time to month.. and value to amo_sample
```{r}
colnames(amo_yrmt)[2] <- "month"
colnames(amo_yrmt)[3] <- "amo_sample"
amo_yrmt
write.csv(amo_yrmt, "../output/env/amo_yrmt.csv") # written for reuse with the background points 
```

@@

nao_yrmt <- nao_yrmt[order(nao_yrmt$year),] #changed amo to nao
nao_yrmt
```
